\newpage
\section*{\centering Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

I sincerely thank the following people and institutions for assisting me in finishing this study report.

First and foremost, I extend my heartfelt thanks to my placement mentor, T.A.D.A.E Jayathilake, the Chemist at the Wastewater Treatment Plant Moratuwa/ Ratmalana, for her invaluable guidance and unwavering support throughout the duration of my placement.

I am also deeply grateful to my academic mentor, Dr. Ayomi Witharana, Senior Lecturer of Zoology and Environmental Sciences, for insightful advice, encouragement, and constructive feedback which have greatly enriched the quality of this research.

I extend my appreciation to the National Water and Drainage Board for providing access to essential data and resources relevant to this study. Furthermore, I would like to express my gratitude to the staff members, especially the lab assistant and technicians of the Wastewater Treatment Plant, Moratuwa/ Ratmalana who provided valuable information about the plant operations.

Also, I would like to express my gratitude to my brother, U.A.C Perera, and my friend, W.M.S.H Warnasooriya for assisting me in producing the final report and motivating me to successfully finish the project.

Finally, I would like to thank my family and my university colleagues for their unwavering support, understanding, and encouragement throughout this journey. Their love and encouragement have been my constant source of strength.

This research would not have been possible without the collective support and encouragement of all those mentioned above. Thank you for being a part of this journey and for your invaluable contributions.

\clearpage